---
output: github_document
---


# RobStabR

RobStabR is a robust model selection framework for Generalised Linear Models by Connor Smith, Boris  Guennewig and Samuel Müller.

This GitHub is a repository for the R package RobStab R.

# Installation
``` r
library(devtools)
devtools::install_github("SmithConnor/RobStabR")
```

# An example
We have data with 64 observations and 8 variables, and we desire to perform variables selection using the poisson model.
We induce outliers in the 8 observations where X8 is the largest by setting lambda = 5.

```{r, eval = TRUE}
library(RobStabR)

set.seed(15)
n = 64
p = 8
beta = c(1, -1, 1, 
         rep(0, p - 3))
x = matrix(rnorm(n*p), 
           nrow = n,
           ncol = p)
colnames(x) = paste0("X", 
                     1:p)
lambda = exp(x %*% beta)
lambda[which(rank(x[,8]) <= 8)] = 5 # Induce outliers
y = rpois(n = n, 
          lambda = lambda)
data = data.frame(x, y)
robStabResult = RobStabR::model_space(data = data,
                                      B = 100,
                                      m = n/2,
                                      family = poisson(link = "log"),
                                      tcc = 2)

robStabResult$dev
```

The best model selected byt the RDBC when the penalty is P2 is:

```{r, eval = TRUE}
robStabResult$dev[which.min(robStabResult$dev$P2),]
```


