---
author: "Connor Smith"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{""}
  %\usepackage[UTF-8]{inputenc}
---

# Hospitcal Costs Analysis

Load required packages.
```{r warning=FALSE, message=FALSE}
library("robmixglm")
library("magrittr")
library("dplyr")

library(devtools)
# install_github("SmithConnor/RobStabR")
library("RobStabR")
```

Load Hospital costs data.

```{r datawrangling}
utils::data("hospcosts", package ="robmixglm")

data = hospcosts %>% 
  dplyr::mutate(y = costs) %>% 
  dplyr::select(-id, - costs, -los)
```

## Robust Plots

Repeat the analysis completed in the manuscript using the exact same bootstraps with robust regression.

```{r fitRobStab}
paperRobStab = readRDS("./../manuscript/hosp_robust_RobStab.rds") # Analysis done for the manuscript

resamplePaper = paperRobStab$bootsrap

hospRobStab = model_space(data = data,
                          B = 100,
                          m = 50,
                          nStrata = 5,
                          family = Gamma(link = log),
                          tcc = 1.5,
                          bootstraps = resamplePaper)
```

Construct the robust subtractive Variable Inclusion Plot.

```{r rsVIP, fig.height = 4, fig.width = 7, fig.align = "center"}
hospMPP = sMPP(robStab = hospRobStab)
hospMPP$plots$dev
```

Construct the robust subtractive Mosaic Probability Plot.

```{r rsMPP, fig.height = 4, fig.width = 7, fig.align = "center"}
hospVIP = sVIP(robStab = hospRobStab)
hospVIP$plots$dev
```

## Non-Robust Plots

Repeat the analysis completed in the manuscript using the exact same bootstraps with non-robust regression.

```{r fitRobStabNon}
paperRobStab2 = readRDS("./../manuscript/hosp_RobStab.rds") # Analysis done for the manuscript

resamplePaper2 = paperRobStab2$bootsrap

hospRobStabNon = model_space_non(data = data,
                          B = 100,
                          m = 50,
                          nStrata = 5,
                          family = Gamma(link = log),
                          bootstraps = resamplePaper2)
```

Construct the non-robust subtractive Variable Inclusion Plot.

```{r sVIP, fig.height = 4, fig.width = 7, fig.align = "center"}
hospMPP = sMPP(robStab = hospRobStabNon)
hospMPP$plots$dev
```

Construct the non-robust subtractive Mosaic Probability Plot.

```{r sMPP, fig.height = 4, fig.width = 7, fig.align = "center"}
hospVIP = sVIP(robStab = hospRobStabNon)
hospVIP$plots$dev
```

